# P6: Exploring Prosper Loan Dataset
Author: Ying Wu

# Introduction
Prosper is a company that offers a marketplace for peer to peer lending.
Individuals can request loans and Prosper will calculate a score value
indicating the risk of the loan the individual is asking for and then 
add that loan into their system. Investors can choose the type of loans 
that they would want to get exposure to allowing them to trade off risk 
for return.

My goal is to pick out an interesting facet of this loan data and explore
it further using a d3.js visualization.

# Exploration

Looking through the variable definitions, I was most intrigued by the categories.
I exploring the relationship between these categories and the rest of the 
variables available in the Prosper loan data.

```{r readin}
library(data.table)
library(ggplot2)
# dt = fread("prosperLoanData.csv") # everything is character
df = read.table("prosperLoanData.csv", header=T, sep=",")
dt = as.data.table(df)
rm(df)

dt$ListingNumber = as.factor(dt$ListingNumber)
dt$ListingCreationDate = as.POSIXct(dt$ListingCreationDate)
dt$Term = as.factor(dt$Term)
dt$ClosedDate = as.Date(dt$ClosedDate)
dt$ListingCategory..numeric. = factor(dt$ListingCategory..numeric.)
levels(dt$ListingCategory..numeric.) = c(NA, "Debt Consolidation", "Home Improvement", "Business", "Personal Loan", 
  "Student Use", "Auto", "Other", "Baby&Adoption", "Boat", "Cosmetic Procedure",
  "Engagement Ring", "Green Loans", "Household Expenses", "Large Purchases",
  "Medical/Dental", "Motorcycle", "RV", "Taxes", "Vacation", "Wedding Loans")
dt$DateCreditPulled = as.POSIXct(dt$DateCreditPulled)
dt$FirstRecordedCreditLine = as.Date(dt$FirstRecordedCreditLine)
dt$LoanOriginationDate = as.Date(dt$LoanOriginationDate)

dt$IncomeRange = ordered(dt$IncomeRange, levels(dt$IncomeRange)[c(8, 1, 3, 4, 5, 6, 2, 7)])

summary(dt)
```

Some data summaries and reading online reveals that Prosper changed their API in
the latter half of 2009. In order to have the most consistant dataset, I exclude
data from before this period. I believe the most interesting comparison with 
ListingCategory is the IncomeRange of the inviduals asking for the loan

```{r summary1}
table(dt[ListingCreationDate > "2009-07-01"]$ListingCategory..numeric., dt[ListingCreationDate > "2009-07-01"]$IncomeRange)

ggplot(dt[ListingCreationDate > "2009-07-01"], aes(ListingCategory..numeric., fill = IncomeRange)) + geom_bar() + coord_flip()

setnames(dt, "ListingCategory..numeric.", "ListingCategory")
```

merge income ranges and summarize
```{r summary2}
tmp = dt[ListingCreationDate > "2009-07-01", list(Total = .N), by = list(ListingCategory, IncomeRange)]
out = dcast(tmp, ListingCategory ~ IncomeRange, value.var = "Total", fill = 0)
out$LowIncome = out$"Not employed" + out$"$0" + out$"$1-24,999"
out$MiddleIncome = out$"$25,000-49,999" + out$"$50,000-74,999"
out$HighIncome = out$"$75,000-99,999" + out$"$100,000+"
out[, Total := LowIncome + MiddleIncome + HighIncome]
out[, LowIncomePct := round(LowIncome / Total, 3)]
out[, MiddleIncomePct := round(MiddleIncome / Total, 3)]
out[, HighIncomePct := 1 - MiddleIncomePct - LowIncomePct] # so all sum to 1
out = out[ListingCategory != "Other"] # remove NA and "Other" since uninformative
setorder(out, HighIncomePct)
out$ListingCategory = factor(out$ListingCategory, levels = as.character(out$ListingCategory)) # reorder

ggplot(melt(out, id.vars = "ListingCategory", measure.vars = c("LowIncomePct", "MiddleIncomePct", "HighIncomePct")), 
	aes(ListingCategory, value, fill = variable)) + geom_bar(stat = 'identity') + coord_flip()
```

write out the data
```{r output, eval = FALSE}

# cleanup
out = out[, .(ListingCategory, LowIncomePct, MiddleIncomePct, HighIncomePct, Total)]
setnames(out, c("ListingCategory", "LowIncome <$25k", "MiddleIncome", "HighIncome >$75k", "Total"))
write.csv(out, file = "data.csv", row.names = FALSE)
```

# Summary
Thinking from a perspective of an affliate advertiser, my goal is to identify 
target audiences that might be interested in lending using Prosper based off
historical loan data. To achieve this, I identified two interesting variables
in the Prosper dataset: ListingCategory and IncomeRange. The former provides
good sites to place ads for Prosper whereas the latter can be used to filter
the customers to target these advertisements for.

Based on the data, I found that the following class of individuals 
would be a good target for Prosper ads:
- Low income students
- Middle income looking for cosmetic procedures
- High income in months before taxes being due

These three categories are specific to each income category. Sorting by
high income: Taxes have the highest percentage while Cosmetic Procedure
and Student Use are the lowest. Sorting by middle income: Cosmetic Procedure
had the highest percentage while Student Use and Taxes were the lowest.
Sorting by low income: Student Use by far had the highest percentage
with Taxes near the bottom and Cosmetic Procedure in the middle.

# Design
I used a proportional stacked bar chart to show the number of loans for a 
given category and IncomeRange. The IncomeRange is encoded using different 
colors in a gradient to show the ordinal nature of this variable.

For interactive component, I added in a mouseover tooltip on the Y-axis to 
allow the user to see how many elements there were total. In addition, another
mouseover showed the percentage of every income class.

After collecting feedback on the initial version, I realized that I needed a
better mechanism to emphasize the differences between the income classes. I added
a dropdown menu to sort by different income classes to emphasize the differences
between income classes. Additionally, I bolded the categories of interest and
I sorted by Low income by default since "Student Use" had the most striking 
example of percentage overrepresentation by income class.

# Feedback

I asked the following questions and wrote down the respones below:

- What do you notice in the visualization?
- What questions do you have about the data?
- What relationships do you notice?
- What do you think is the main takeaway from this visualization?
- Is there something you don’t understand in the graphic?

## Feedback 1 - Lynn

Poor students are one of the highest proportions.

Could you sort by the other income classes too (low and middle)?

Middle income seems to dominate Cosmetic Procedure and transportation related
(Auto and Motorcycle).

Poor students would be a good target for Prosper advertisements.

I understand the graphic.

## Feedback 2 - Jamie
Middle income has the largest % of loans

Could you also show the dollar amount of each loan?

Low income have disporportionately high student loans

I understand the graphic.

## Feedback 3 - Jo

The difference between what poor people ask for loans on and what rich people
ask for loans on is quite big.

Could you sort by low income instead of high?

Why students getting loans from Prosper rather than regular student loans.

Low income is more likely to use prosper for student loans. Middle income for 
status symbol items like beauty, and cars. High income for home improvement or taxes.

I understand the graphic. 

# Resources
https://developers.prosper.com/docs/investor/loans-api/

http://square.github.io/intro-to-d3/

https://github.com/d3/d3/wiki/

https://bl.ocks.org/mbostock/3886208 

https://github.com/d3/d3/blob/master/API.md

various stackoverflow and plnkr/jsfiddle/bl.ocks examples